Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-22 paper/paper.tex
Add skips to correctly position all plots
Fix issues

\title{Measuring Software Ticket Quality using Quantitative Data Analysis}
\author{Andrei-Mihai Nicolae}
\matricnum{21473292}

@@

\begin{abstract}
Issue trackins systems have become the defacto standard for tracking work items in 
software projects - they guide engineers towards better planning and 
managing their progress throughout complex projects. However, there
are few studies that investigate what makes for a high quality,
valuable ticket. This can lead to multiple issues in a company, such as 
increased communication friction between developers and end users filing bug
reports, as well as increased overall costs due to waste of development effort. 
In this research paper, we present our findings after 
investigating a large number of variables surrounding software tickets, 
Our results show that the presence and type of attachments,
comments complexity, summary and description complexity, presence of stack traces, presence
of steps to reproduce, grammar correctness scores, as well as sentiment can significantly influence 
the quality of the ticket. We supply one of the largest dataset statistically 
analysed in this particular field, as well as state-of-the-art sentiment and grammar correctness analyses.
\end{abstract}

@@

In the past decade software projects have inherently become more complex and require increasing number of developers in
the team. Studies such as the one conducted by Herbsleb \cite{herbsleb2007global} show how software engineering teams have 
transitioned from small, collocated to globally distributed teams. One reason elicited in the paper is the increasing 
popularity of communication tools, such as Slack or Google Hangouts. Due to this, developers have created issue tracking 
systems as means of planning, managing and tracking work products in the form of \emph{software tickets} or \emph{issues}.

@@

@@

@@

@@

>>>>

\title{Measuring Software Ticket Quality using Quantitative Data Analysis}
\author{Andrei-Mihai Nicolae}
\matricnum{2147392}

@@

\begin{abstract}
Issue tracking systems have become the defacto standard for tracking work items in 
software projects - they guide engineers towards better planning and 
managing their progress throughout complex projects. However, there
are few studies that investigate what makes for a high quality,
valuable ticket. This can lead to multiple issues in a company, such as 
increased communication friction between developers and end users filing bug
reports, as well as increased overall costs due to waste of development effort. 
In this research paper, we present our findings after 
investigating a large number of variables surrounding software tickets.
Our results show that the presence and type of attachments,
comments complexity, summary and description complexity, presence of stack traces, presence
of steps to reproduce, grammar correctness scores, as well as sentiment can significantly influence 
the quality of the ticket. We supply one of the largest dataset statistically 
analysed in this particular field, as well as state-of-the-art sentiment and grammar correctness analyses.
\end{abstract}

@@

In the past decade software projects have inherently become more complex and they now require increasing number of developers in
the team. Studies such as the one conducted by Herbsleb \cite{herbsleb2007global} show how software engineering teams have 
transitioned from small, collocated to globally distributed teams. One reason elicited in the paper is the increasing 
popularity of communication tools, such as Slack or Google Hangouts. Due to this, developers have created issue tracking 
systems as means of planning, managing and tracking work products in the form of \emph{software tickets} or \emph{issues}.

@@

\vskip30pt

@@

\vskip18pt

@@

\vskip12pt

@@

\vskip10pt
